---
title: "Data Quality Assessment"
author: "Sasa Lukic"
date: "5 11 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Load libraries

library(arules)
library(arulesViz)
library(dplyr)
library(tidyverse)
library(plyr)
library(RColorBrewer)

```

```{r}
# Load data

line_item <- read.csv("line_item.csv")
orders <- read.csv("orders.csv")
products <- read.csv("products.csv")

```


```{r}

# Check for missing values

sum(is.na(c(line_item, orders, products)))

```

# Summarise data

```{r}

glimpse(c(line_item, orders, products))

summary(c(line_item, orders, products))

str(c(line_item, orders, products))

```


# Joining and filtering data

```{r}

complete <- inner_join(line_item, orders, by="id_order")

complete <- inner_join(complete, products, by="sku")

complete <- filter(complete, state=="Completed")
```

## grouping by id_order
## calculating difference in the total amount paid

```{r}

difference <- line_item %>% 
  select(id_order, unit_price, product_quantity) %>% 
  group_by(id_order) %>%
  mutate(order_sum=unit_price * product_quantity)

```

# Explore diference between order sum and total paid

```{r}

difference_paid <- inner_join(difference, orders, by="id_order")

difference_paid <- mutate(difference_paid, total_diff = total_paid - order_sum)

difference_paid <- mutate(difference_paid, ratio=round((total_diff/total_paid) * 100),2)

difference_paid <- filter(difference_paid, ratio<20)

difference_paid <- filter(difference_paid, ratio>-20)

```

# Filter data from complete based on exploration


```{r}

complete <- filter(complete, id_order %in% difference_paid$id_order)

```

# Explore difference between unit price and price

```{r}

difference_price <- select(complete, id_order, unit_price, price)

difference_price <- mutate(difference_price, diff_new = price - unit_price)

difference_price <- mutate(difference_price, diff_ratio = round((diff_new/price) * 100), 2)

difference_price <- filter(difference_price, diff_ratio<20)

difference_price <- filter(difference_price, diff_ratio>-20)

```

# Filter data from complete based on exploration

```{r}

complete <- filter(complete, id_order %in% difference_price$id_order)

```

# Create final table for creating transaction file and write csv

```{r}

complete <- select(complete, id_order, sku)

complete <- ddply(complete,c("id_order"),
                       function(df1)paste(df1$sku,
                       collapse = ","))

complete$id_order <- NULL
```


```{r}
write.csv(complete, 
          file = "transactions.csv",
          row.names=FALSE, quote = FALSE)
```

# Create transactional file

```{r}

tr <- read.transactions(
  file = "transactions.csv",
  format = "single",
  cols = c(1,2),
  header = TRUE,
  sep = ",")
```

# Summary and inspect of tr

```{r}

summary(tr)

```

```{r}

inspect(tr[1:20])

length(tr) # Number of transactions. 

size(tr) # Number of items per transaction 

LIST(tr) # Lists the transactions by conversion (LIST must be capitalized)

itemLabels(tr) # To see the item labels 

```

# Visualize transactions

```{r}

itemFrequencyPlot(tr,topN=20,type="absolute",col=brewer.pal(8,'Pastel2'), main="Absolute Item Frequency Plot")



```

# Create rules using apriori algorithm

```{r}

association.rules <- apriori(tr, parameter = list(supp=0.001, conf=0.8))


```

```{r}

summary(association.rules)

inspect(association.rules[1:10])
```
